### 2016-11-04 paper/evaluation.tex
reorganized par from rq1
fixed text to decrease order

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision. Results indicate
that a relatively high number of projects from the sample set requires
at least five minutes to execute. The longest execution takes \Fix{x}
to finish.

@@

To evaluate the distribution of execution time per project, we sorted
the test cases by increasing order of elapsed time and calculated the
number of tests executed in 90\% of the total time. Later, we reported
the \Fix{balance} of execution time by dividing the number of tests
that represents 90\% of the execution time by the number of tests
cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
collected the elapsed time from test cases for each generated report.
Maven Surefire generates an XML report with execution information
(\eg, number of skipped tests and elapsed time) per test suite
\Jbc{Should I use the previous sentence as a footnote or should I
delete it?}. We noticed that some test cases reported an elapsed time
of zero: since the reported time is in milliseconds, some tests may
execute in a shorter time. \Fix{..to be continued...}}. Results
indicate that \Fix{...}.

>>>>

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group.  Results indicate that a relatively
high number of projects from the sample set requires at least five
minutes to execute. The longest execution takes \Fix{x} to finish. It
is important to mention that Figure~\ref{fig:piechart-time} represents
a lower bound for elapsed time: some tests may finish early due to a
failure since the subjects were tested in a potentially unstable
revision.

@@

To evaluate the distribution of execution time per project, we sorted
the test cases by decreasing order of elapsed time and calculated the
number of tests executed in 90\% of the total time. Later, we reported
the \Fix{balance} of execution time by dividing the number of tests
that represents 90\% of the execution time by the number of tests
cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
collected the elapsed time from test cases for each generated report.
Maven Surefire generates an XML report with execution information
(\eg, number of skipped tests and elapsed time) per test suite
\Jbc{Should I use the previous sentence as a footnote or should I
delete it?}. We noticed that some test cases reported an elapsed time
of zero: since the reported time is in milliseconds, some tests may
execute in a shorter time. \Fix{..to be continued...}}. Results
indicate that \Fix{...}.
